EDLD 651 Final Project Presentation

### 2020-12-02 presentation.Rmd
last minute update

## Victories and celebrations
- making GIFs
- super neat plots
- research question was answered
- hypothesis was correct
- using R to make this presentation

## Remaining Challenges
- make some plots prettier

## Next R hurdle to tackle
- remove outliers and re-run analysis
- run a power analysis
- work with the "random" data
- adapt and develop the study
- run an online study
- replicate with cellular automata and 3D dynamic fractals

>>>>

## Victories and celebrations
- making GIFs
- super neat plots
- proof of concept and task
- research question was answered
- hypothesis was correct
- using R to make this presentation

## Next R hurdle to tackle
- remove outliers and re-run analysis
- run a power analysis
- work with the "random" data
- make some plots prettier

## Remaining Challenges
- adapt and develop the study
- run an online study
- 3D dynamic fractals
- replicate with cellular automata
